### 2015-04-12 latex/phd_thesis.tex
Add chapter abstract macro
Update date :(

@@

\author{{\bf \Large Peter Francis Hickey}\\\\
Submitted in total fulfilment of the requirements\\
of the degree of Doctor of Philosophy\\\\
March 2015\\\\
Department of Mathematics and Statistics\\
The University of Melbourne\\\\}

>>>>

% Chapter abstracts (http://tex.stackexchange.com/a/59138)
\usepackage{changepage}% http://ctan.org/pkg/changepage
\usepackage{lipsum}% http://ctan.org/pkg/lipsum
\makeatletter
\newenvironment{chapabstract}{%
    \begin{center}%
      \bfseries Overview
    \end{center}}%
   {\par}
\makeatother

@@

\author{{\bf \Large Peter Francis Hickey}\\\\
Submitted in total fulfilment of the requirements\\
of the degree of Doctor of Philosophy\\\\
April 2015\\\\
Department of Mathematics and Statistics\\
The University of Melbourne\\\\}
